Impact of LAIV on School Absenteeism

### 2016-09-19 paper.Rmd
minor changes, new chart

# Get non flu season absenteeism for each person
nfsa <- 
  df %>%
  filter(!flu_season) %>%
  group_by(id) %>%
  summarise(nfsa = length(which(absent)),
            eligibles = length(absent)) %>%
  mutate(nfsar = nfsa / eligibles * 100) %>%
  dplyr::select(id, nfsar)
df <- left_join(df, nfsa, by = 'id')
```

@@

>>>>

# Get non flu season absenteeism for each person
nfsa <- 
  df %>%
  filter(!flu_season) %>%
  group_by(id) %>%
  summarise(nfsa = length(which(absent)),
            eligibles = length(absent),
            school = first(school),
            grade = first(grade)) %>%
  mutate(nfsar = nfsa / eligibles * 100) %>%
  dplyr::select(id, nfsar)
df <- left_join(df, nfsa, by = 'id')
```

@@

### Visualizing

The below chart shows school-grade specific flu season absenteeism as a function of immunization rate

```{r}
temp <-
  df %>%
  filter(flu_season) %>%
  group_by(school, grade) %>%
  summarise(absences = length(which(absent)),
            vaccinations = length(unique(id[vaccine])),
            students = length(unique(id)),
            eligibles = n()) %>%
  mutate(immunization_rate = vaccinations / students * 100,
         absenteeism_rate = absences / eligibles * 100) %>%
  rename(Grade = grade,
         Students = students)

# Get school grade combo
temp$school_grade <- paste0(temp$school, ' ', temp$Grade)

# Remove those not affected by program
temp <- temp %>% filter(immunization_rate > 0)

g <- ggplot(data = temp,
       aes(x = immunization_rate,
           y = absenteeism_rate)) +
  geom_point(aes(size = Students,
             color = Grade),
             alpha = 0.6) +
  xlab('Immunization rate') +
  ylab('Absenteeism rate') +
  theme_economist() +
  ggtitle('Association between immunization and flu season absenteeism',
          'Each dot represents one grade at one school') +
  ylim(0, 20)
print(g)
ggsave('~/Desktop/chart_for_parker.pdf')
print(g + scale_y_log10())

### Modeling
